%% start of file `template.tex'.
%% Copyright 2006-2010 Xavier Danaux (xdanaux@gmail.com).
%% Copyright 2010-2011 Mark Liu (markwayneliu@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.

\documentclass[11pt,a4paper,sans]{moderncv}

\usepackage{verbatim}

% moderncv themes
\moderncvstyle{classic}
\moderncvcolor{blue}

% character encoding
\usepackage[utf8]{inputenc}                   % replace by the encoding you are using

% adjust the page margins
\usepackage[scale=0.8]{geometry}
%\setlength{\hintscolumnwidth}{3cm}						% if you want to change the width of the column with the dates
%\AtBeginDocument{\setlength{\maketitlenamewidth}{6cm}}  % only for the classic theme, if you want to change the width of your name placeholder (to leave more space for your address details
%\AtBeginDocument{\recomputelengths}                     % required when changes are made to page layout lengths


% personal data
\firstname{Vivek Kumar}
\familyname{Thakur}
\address{210-A , Boys Hostel}{Army Institute of Technology,Pune}    % optional, remove the line if not wanted
\mobile{9421701789}                    % optional, remove the line if not wanted
\email{vivekkthakur\_12192@aitpune.edu.in}                      % optional, remove the line if not wanted
\homepage{http://www.algorithms4geeks.blogspot.com}                % optional, remove the line if not wanted
\extrainfo{\url{https://github.com/vkthakur}} % optional, remove the line if not wanted

% to show numerical labels in the bibliography; only useful if you make citations in your resume
%\makeatletter
%\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
%\makeatother

%\nopagenumbers{}                             % uncomment to suppress automatic page numbering for CVs longer than one page
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
\maketitle

\section{Objective}

Obtain an intensive software development summer internship that utilizes my data structures,algorithmic skills to make the company's product better for its users.

\section{Education}
\cventry{2012--2016}{BE,Computer Engineering}{Army Institute of Technology}{Pune,Maharashtra}{}{}
\cvline{Aggregate:}{\small 68.8\% Till 4th Semester}
\cventry{2011}{Intermediate/+2}{Kendriya Vidyalaya Lucknow Cantt}{Lucknow,UP}{}{}
\cvline{Aggregate:}{\small 89.9\%}
\cventry{2009}{Matriculation/10th}{Kendriya Vidyalaya Lucknow Cantt}{Lucknow,UP}{}{}  % arguments 3 to 6 can be left empty
\cvline{Aggregate:}{\small 86.6\%}



\section{Interests}

Algorithms ,Data Structures ,Programming Contests.


\section{Technical Skills}

\cvline{Languages}{C, C++, Python,Java.}
\cvline{Platforms}{Linux ,Microsoft Windows.}

\section{Projects}
\subsection{Online Typing Test}
\cvline{Description}{It is a web application developed in JSP and MongoDB for analysing user's typing speed along with accuracy.User has to pass certain 
criteria to advance to next level.
}

\subsection{Optimal Text Search}
\cvline{Description}{An Algorithm to extract some set of random words from a given dictionary such that the letter count requirement is fulfilled.I implemented it using trie data structure in Qt framework.Also a comparison on the basis of time consumption between
naive algorithm and the algorithm using tries.
}
\subsection{GupShup}
\cvline{Description}{An application layer networking application designed for instant messenging in the Local Area Network(wired or wireless) based on STAR topology using multithreaded server.
}
\subsection{Online Compiler ( www.onlinecompiler.wc.lt ) }
\cvline{Description}{Using Ideone API built an online website where codes can be compiled in over 100 languages.
}

\section{Achievements}
\subsection{Tech-Aakriti 2013-2014}
\cvline{}{Came 1st in Inter-Branch coding competition at Army Institute Of Technology.
}
\subsection{Solution'13}
\cvline{}{Came 1st in Inter-College coding event at AIT SOLUTION’S 13.
}
\subsection{Solution'13}
\cvline{}{Secured 1 in inter-college debugging event at AIT SOLUTION’S 13.
}
\subsection{OSS Club Coding Competition}
\cvline{}{Came 3rd in coding competition at AIT (2013-2014) organized by OSS club.
}
\section{Rating At Different Coding Sites:}
\cvline{Codechef}{ handle: vthakur
	long contest : 2462.84
	Short Contest: 1266.79
}
\cvline{Codeforces}{ handle: vkthakur
	Rating: 1224	
}
\cvline{Spoj}{ handle: vkthakur
	Rank: 7350	
}

\section{Work Experience: }
\cvline{Problem Setter}{ Set problems for algorithmic programming contests for college's internal contests like Tech-Aakriti and Solution.
}

\section{Hobbies:}
\cvline{}{ Blogging: http://algorithms4geeks.blogspot.in
}
\cvline{}{ Competitive Programming
}
\cvline{}{  BasketBall (Regional Level Lucknow)
}

\section{Extra-Curricular Activities:}
\cvline{}{ Playing Basketball from Computer Branch.
}

\cvline{}{ Secured 2nd in Cross-Country (Computer).
}

\cvline{}{  Played Basketball at Regional Level in 2008-2009 and 2010-2011.
}

\cvline{}{  Event Head of Codered and debugging for Tech-Aakriti 2014-2015 .
}




	


\end{document}
